---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

NOTE: This package is very much experimental in nature and should be treated as
such until the 0.1.0 release. 

super is a fork / reimplementation of the [glue](https://glue.tidyverse.org)
package with a focus on efficiency and simplicity at a cost of flexibility.

## Installing the package

You can install the latest release of super from [CRAN](https://cran.r-project.org/) with:

```{r, eval = FALSE}
install.packages("super")
```

The development version can be installed from r-universe with:

```{r, eval = FALSE}
install.packages(
    'super',
    repos = c('https://timtaylor.r-universe.dev', 'https://cloud.r-project.org')
)
```

## Vignettes

An brief overview of super is provided in the vignette distributed with the
package:

* `vignette("super", package = "super")`
